\documentclass[notes]{beamer}
\usepackage{hyperref}
\usepackage{graphicx}
\mode<article>
    {
      \usepackage{fullpage}
      \usepackage{pdf}
      \usepackage{hyperref}
    }
    
\mode<presentation>{
  \usetheme{Dresden}
  \setbeamercovered{transparent}
}

\title{HacDC}
\author{Serge Wroclawski}
\begin{document}
\section{The Objective}

\begin{frame}
  \frametitle{What is HacDC?}
  From \href{http://www.hacdc.org}{hacdc.org}:
  \begin{quote}
    HacDC is a non-profit organization and space dedicated to
    technical, artistic and social collaboration. We are
    technologists, tinkerers, crafters and codemonkeys who call DC
    home. We collaborate across disciplines for the benefit of
    cultural, charitable and scientific causes. We create, learn and
    teach as a group, inviting our neighbors around the block and
    around the world to join us.
  \end{quote}
\end{frame}

\begin{frame}
  \frametitle{Does HacDC Do?}
  \begin{itemize}
  \item Provides a workshop for people to work on ongoing projects
  \item New Workshop Coming Soon!
  \item Provides a meeting space for groups
  \item An organization to bring communities together
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Does HacDC Do?}
  \begin{itemize}
  \item Provides a workshop for people to work on ongoing projects
    \uncover<3>{
    \begin{itemize}
    \item Lots of free parts of every sort (motors, cables, raw materials)
    \item A stocked pantry of low-cost parts (IC chips, microcontrollers, LEDs)
    \item Free supplemental parts (solder, wire)
    \item Lots of tools!
    \end{itemize}
    }
  \item New Workshop Coming Soon!
    \uncover<4>{
    \begin{itemize}
    \item New Workshop being built in basement
    \item Will allow for larger projects (possible wood or metal-working)
    \end{itemize}
    }
  \item Provides a meeting space for groups
    \uncover<5>{
    \begin{itemize}
    \item The Workshop, Church Auditorium, Church Dining Room
    \end{itemize}
  }
  \item An organization to bring communities together
    \uncover<5>{
    \begin{itemize}
    \item Software People
    \item Hardware People
    \item Artists
    \end{itemize}
  }
  \end{itemize}
\end{frame}


% \section{The Space}

%\section{The Activities}

%\section{Getting Involved}
\end{document}